COMPAS Race Analysis

### 2022-04-28 Markdown Files Sprints 3 and 4/race compas analysis.Rmd

```{r py setup, include=FALSE}
library(reticulate)
```

```{python import, include= FALSE}
import matplotlib.pyplot as plt
import matplotlib.patches as patches
import numpy as np
import pandas as pd
import seaborn as sns

@@

from IPython.display import Markdown, display
```

>>>>

```{r py setup, include=FALSE}
library(reticulate)
use_condaenv("base")
#if (grepl("dcaravela", Sys.getenv("HOME"))) {
 # use_condaenv("base")
#}
```

```{python import, include= FALSE}
#import matplotlib.pyplot as plt
import matplotlib.patches as patches
import numpy as np
import pandas as pd
import seaborn as sns

@@

#from IPython.display import Markdown, display
```
